Lens Modeling in \sw

### 2014-01-24 text/ms.tex

Our present picture of the formation of the largest structures in the
Universe --- galaxies and clusters of galaxies --- is that
gravitational instabilities (whose early stages are observable as
fluctuations of the microwave background) caused a collapse into
gravitationally bound structures.  Dark matter would have dominated
the initial collapse, but once deep wells in the gravitational
potential appeared, gas would have fallen into them while radiating
away its gravitational potential energy through atomic processes to
form the first stars and galaxies.  With time, galaxies and clusters
would continue to merge and change their form.  This rough outline is
well-established now, but many puzzles remain to be solved before our
understanding is satisfactory.  To progress towards solving these, we
need more knowledge of dark matter.  And to study dark matter,
gravitational lensing is attractive, because it depends only on mass.

>>>>

Galaxies and clusters of galaxies are considered to be the largest structures in the known Universe. When one questions their formation,  the present picture suggests that gravitational instabilities  (observable as fluctuations of the microwave background) 
 \todo[red]{not too sure of the relevance of this statement} 
 - caused a collapse into gravitationally bound structures. 
 \todo[yellow]{clarification needed: are they becoming gravitationally bound structures, or are they collapsing into objects that are already gravitationally bound? I know it is most probably the later, but it is a bit ambiguous}   
The initial collapse would have been dominated by dark matter, but once deep wells had appeared in the gravitational potential, gas would have started falling into those wells. 
\todo[red]{not too sure of this wording}
Through atomic processes,
\todo[yellow]{perhaps we need to clarify those processes or are they generally know?}
 the gravitational potential energy of this gas would of been radiated away, leading to the formation of the largest stars. 
\todo[red]{or perhaps just stars?}
In turn, galaxies and clusters of galaxies would form, all the time merging and changing their form.
This rough outline is now well established, but in order to satisfy our understanding of this process, there are many puzzles  that remain to be solved. For progress to be made, we need to extend our knowledge of dark matter. Gravitational lensing has proven as a particularly attractive way of studying dark matter as it is only dependant on mass.
\todo[yellow]{silly question, but shouldn't we briefly explain why it is only dependant on mass? or should everyone already reading this paper know that? or is it explained later?}
